PANCHANGE_data_preprocessing

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Finished adapting MHD depression, anxiety, and eating disorder sections for NBR.

@@

```{r mhd depressive_disorders}
## CHECK THAT THIS CHUNK WORKS FOR EDGI AS WELL (confirmed that it works for NBR)
if(GLAD = TRUE | EDGI = TRUE | NBR = TRUE)
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    depressive_disorders_numeric =
      case_when(
        (mhd.depression_numeric == "0" &
        (mhd.pregnancy_depression_numeric == "0" | is.na(mhd.pregnancy_depression_numeric)) & 
        (mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhd.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
        mhd.depression_numeric == "1" ~ 1,
        mhd.pregnancy_depression_numeric == "1" ~ 1,
        mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))

@@

```{r Check depressive_disorders}
mhd.raw.id %>%
  select(
    depressive_disorders,
    depressive_disorders_numeric,
    mhd.depression_numeric,
    mhd.pregnancy_depression_numeric,
    mhd.premenstrual_dysphoric_disorder_pmdd_numeric,
    mhd.depression,
    mhd.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd
  )
```

Anxiety disorders group
```{r glad mhd anxiety_disorders}
if(GLAD = TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    anxiety_disorders_numeric =
      case_when(
        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
        mhd.social_anxiety_or_social_phobia_numeric == "0" &
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
        mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

@@

```{r nbr mhd anxiety_disorders}
if(NBR = TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    anxiety_disorders_numeric =
      case_when(
        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
        mhd.social_anxiety_or_social_phobia_numeric == "0" &
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
        mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

```{r Check anxiety_disorders}
mhd.raw.id %>%
  select(
    anxiety_disorders,
    anxiety_disorders_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
```

Agoraphonia and panic disorder group
```{r glad mhd agoraphobia_panic_disorder}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    agoraphobia_panic_disorder_numeric =
      case_when(
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(agoraphobia_panic_disorder)
```

```{r Check agoraphobia_panic_disorder}
mhd.raw.id %>%
  select(
    agoraphobia_panic_disorder,
    agoraphobia_panic_disorder_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
```

Depression and anxiety comorbidity
```{r glad mhd depression_anxiety}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    depression_and_anxiety_numeric =
      case_when(
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 0 ~ 0,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 1 ~ 1,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 0 ~ 2,
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 1 ~ 3
      )
  )

@@

mhd.raw.id %>%
  freq(depression_and_anxiety,
       cumul = F)
```

Eating disorders group
```{r glad mhd eating_disorders}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 1,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(eating_disorders,
       cumul = F)
```

Eating disorders with binge eating vs eating disorders without
Caveat: Anorexia nervosa can have binge eating as well. Therefore, this would need an additional variable from the ED100K
```{r glad mhd restricting_vs_binge_eating_eating_disorders}
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders_numeric =
      case_when(
                mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 2,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 2,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(restricting_vs_binge_eating_eating_disorders,
       cumul = F)
```

```{r Check eating_disorders}
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.psychological_overeating_or_bingeeating_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating
  )
```

>>>>

# Rename columns that differ from GLAD
nbr.mhd.raw.id <- nbr.mhd.raw.id %>% 
  mutate(
    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric = mhd.specific_phobia_e.g._fear_of_flying_numeric,
    mhd.psychological_overeating_or_bingeeating = mhd.bingeeating_disorder,
    mhd.psychological_overeating_or_bingeeating_numeric = mhd.bingeeating_disorder_numeric
  )

@@

```{r mhd depressive_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE)
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    depressive_disorders_numeric =
      case_when(
        (mhd.depression_numeric == "0" &
        (mhd.pregnancy_depression_numeric == "0" | is.na(mhd.pregnancy_depression_numeric)) & 
        (mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhd.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
        mhd.depression_numeric == "1" ~ 1,
        mhd.pregnancy_depression_numeric == "1" ~ 1,
        mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))

@@

```{r Check depressive_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    depressive_disorders,
    depressive_disorders_numeric,
    mhd.depression_numeric,
    mhd.pregnancy_depression_numeric,
    mhd.premenstrual_dysphoric_disorder_pmdd_numeric,
    mhd.depression,
    mhd.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd
  )
}
```

Anxiety disorders group
```{r mhd anxiety_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    anxiety_disorders_numeric =
      case_when(
        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
        mhd.social_anxiety_or_social_phobia_numeric == "0" &
        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
        mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

@@

```{r Check anxiety_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    anxiety_disorders,
    anxiety_disorders_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
}
```

Agoraphonia and panic disorder group
```{r mhd agoraphobia_panic_disorder}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    agoraphobia_panic_disorder_numeric =
      case_when(
        mhd.agoraphobia_numeric == "1" ~ 1,
        mhd.panic_disorder_numeric == "1" ~ 1,
        mhd.panic_attacks_numeric == "1" ~ 1,
        (mhd.agoraphobia_numeric == "0" &
        mhd.panic_disorder_numeric == "0" &
        mhd.panic_attacks_numeric == "0") ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(agoraphobia_panic_disorder)
}
```

```{r Check agoraphobia_panic_disorder}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    agoraphobia_panic_disorder,
    agoraphobia_panic_disorder_numeric,
    mhd.agoraphobia_numeric,
    mhd.panic_disorder_numeric,
    mhd.panic_attacks_numeric,
    mhd.agoraphobia,
    mhd.panic_disorder,
    mhd.panic_attacks
  )
}
```

Depression and anxiety comorbidity
```{r mhd depression_anxiety}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    depression_and_anxiety_numeric =
      case_when(
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 0 ~ 0,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 1 ~ 1,
        depressive_disorders_numeric == 1 &
          anxiety_disorders_numeric == 0 ~ 2,
        depressive_disorders_numeric == 0 &
          anxiety_disorders_numeric == 1 ~ 3
      )
  )

@@

mhd.raw.id %>%
  freq(depression_and_anxiety,
       cumul = F)
}
```

Eating disorders group
```{r mhd eating_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 1,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(eating_disorders,
       cumul = F)
}
```

Eating disorders with binge eating vs eating disorders without
Caveat: Anorexia nervosa can have binge eating as well. Therefore, this would need an additional variable from the ED100K
```{r mhd restricting_vs_binge_eating_eating_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders_numeric =
      case_when(
                mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 2,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 2,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

@@

mhd.raw.id %>%
  freq(restricting_vs_binge_eating_eating_disorders,
       cumul = F)
}
```

```{r Check eating_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.psychological_overeating_or_bingeeating_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating
  )
}
```
